Finiteness in Cubical Type Theory

### 2020-07-08 sections/topos.tex
added some references
bit more on topos

@@

From here, we can define a notion of isomorphisms.
\begin{agdalisting}
  \ExecuteMetaData[agda/Categories.tex]{isomorphism}
\end{agdalisting}
It's a condition on this type which separates the precategories from the
categories: if it satisfies a form of univalence, it the precategory is a full
category.
\begin{agdalisting}
  \ExecuteMetaData[agda/Categories.tex]{cat-univalence}
\end{agdalisting}

\section{Closure}
\todo{This is just the closure bits pulled over from the finiteness predicates
  section. They need to be reworked to fit in here.}
\subsection{Split Enumerability Closure}
Now that we have a suitable definition of finiteness, we will next prove that
some things are finite.
With the most basic simple types out of the way, the obvious next choice is the
(non-dependent) sums and products: \(\uplus\) and \(\times\).
Both of these types can be constructed from the \emph{dependent} sum, however,
so that is the type we will prove finite.
From that we can derive a much wider array of finiteness proofs.

>>>>

\todo{references here are tricky, need to disentangle the contributions quite
  precisely}
Much of this section is simply a summary of parts of \citet[chapter
9]{hottbook}.
The formal proofs we provide are part translation of those proofs in that
chapter, part from \cite{iversenFredefoxCat2018}
\cite{huProofrelevantCategoryTheory2020}, and part our own.

@@

From here, we can define a notion of isomorphisms.
\begin{agdalisting}
  \ExecuteMetaData[agda/Categories.tex]{isomorphism}
\end{agdalisting}
It's a condition on this type which separates the precategories from the
categories: if it satisfies a form of univalence, it the precategory is a full
category.
\begin{agdalisting}
  \ExecuteMetaData[agda/Categories.tex]{cat-univalence}
\end{agdalisting}
\section{The Category of Sets}
Next we'll look at how to construct the category of sets (in the HoTT sense).
Much of this work comes directly from \citet[chapter 10]{hottbook} and
\citet{rijkeSetsHomotopyType2015}.
The formalisation, however, is novel, as far as we know.

The objects are represented by a \(\Sigma\):
\begin{agdalisting}
  \ExecuteMetaData[agda/Snippets/Category.tex]{hset}
\end{agdalisting}
This will be quite similar to our objects for finite sets.

Since sets in HoTT don't form a topos, there are quite a few smaller lemmas we
need to prove to get as close as we can (a \(\Pi W\)-pretopos): we won't include
them here, other than the closure proofs in the following section.
\section{Closure}
\todo{This is just the closure bits pulled over from the finiteness predicates
  section. They need to be reworked to fit in here.}
\subsection{Split Enumerability Closure}
Now that we have a suitable definition of finiteness, we will next prove that
some things are finite.
With the most basic simple types out of the way, the obvious next choice is the
(non-dependent) sums and products: \(\uplus\) and \(\times\).
Both of these types can be constructed from the \emph{dependent} sum, however,
so that is the type we will prove finite.
From that we can derive a much wider array of finiteness proofs.
